Optimal control for selective electroporation of the viral envelope

### 2021-06-06 documents/pure_electroporation.tex
functioning derivative
symbolic output solution is useless
Trying Differential Evolution

\subsection*{direct method Pseudospectral solvers}

An excellent overview of solutions http://plato.asu.edu/sub/nlounres.html

@@

because the problem depends on the second derivative of sub-nanosecond curves, the scaling varies by about 20 orders of magnitude.
PSOPT [] with IPOPT\cite{implementation2006} solver. PSOPT has the advantage of semi-automatic scaling based on supplied bounds.

@@

@@

software used

@@

@@

>>>>

\subsection*{Pseudospectral solvers}

% is this direct or indirect method?

%An excellent overview of solutions http://plato.asu.edu/sub/nlounres.html - nah, not really that good

@@

Because the problem depends on the second derivative of sub-nanosecond curves, base variable and coefficient scaling varies by more than 20 orders of magnitude.

PSOPT [] with IPOPT\cite{implementation2006} solver. PSOPT has the advantage of semi-automatic scaling based on supplied bounds.

@@

% need to check the required tolerances on the output - how stable is the solution

@@

@@

Extremely speculative and

@@

optimal over a distribution

\subsection{Software used and evaluated:}

casADi;

typeset in LaTeX using TeXstudio.

\subsection{Recommended reading}

de Seze;
